Lens Modeling in \sw

### 2013-11-18 text/tex/results.tex
now tracking figures
Update results.tex
typos

To estimate the performance of the volunteers and the quality of the generated models, two test T1 and T2 were done.

@@

T1 was also designed to give some feedback on the difficulties volunteers encounter, to further imrove the tutorial materials.

>>>>

To estimate the performance of the volunteers and the quality of the generated models, two tests T1 and T2 were done.

@@

T1 was also designed to give some feedback on the difficulties volunteers encounter, to further improve the tutorial materials.
